---
title: "Quarto demonstration."
authors:
  - name: Clint D. Kelly
    affiliations:
      - ref: cdk
    corresponding: true
    email: kelly.clint@uqam.ca
    orcid: 0000-0002-0693-7211
    
affiliations:
  - id: cdk
    name: Département des Sciences biologiques, Université du Québec à Montréal, Montréal, Canada

filters:
  - authors-block

crossref:
  fig-prefix: Figure   # (default is "Figure")
  tbl-prefix: Table    # (default is "Table")

format:
  docx:
    toc: false
    reference-doc: word-style-template.docx
bibliography: Bibliography.bib
csl: evolution.csl
---

```{r echo=FALSE}
knitr::read_chunk('scripts/quarto_demo.R')
```

```{r libraries, include=FALSE,echo=FALSE, warning=FALSE, results="hide"}
```

```{r data_prep, echo=FALSE, warning=FALSE, results="hide", include=FALSE}
```

```{r plot_table, echo=FALSE, warning=FALSE, results="hide", include=FALSE}
```

\newpage

# Abstract

\newpage

# Introduction

# Methods

### Study animals

### Statistical analysis

Post-hoc contrasts are claculated wuing the R package *emmeans* [@lenth2019package].

# Results

## Sex difference in development time

We found a two-way interaction between diet and density (Estimate = `r myround(mean.devtime.brms_fixed[[10,4]],2)` \[`r myround(mean.devtime.brms_fixed[[10,6]],2)`, `r myround(mean.devtime.brms_fixed[[10,7]],2)`\]) that was driven by high density earwigs on a poor diet requiring more time than expected to reach adulthood (interaction contrast: low density vs medium density: $\Delta$$\overline{x}$ = `r myround(summary(mean.devtime.brms.em.contrast)[1,3],2)` \[`r myround(summary(mean.devtime.brms.em.contrast)[1,4],2)`, `r myround(summary(mean.devtime.brms.em.contrast)[1,5],2)`\]; low density vs. high density: $\Delta$$\overline{x}$ = `r myround(summary(mean.devtime.brms.em.contrast)[2,3],2)` \[`r myround(summary(mean.devtime.brms.em.contrast)[2,4],2)`, `r myround(summary(mean.devtime.brms.em.contrast)[2,5],2)`; medium density vs high density: $\Delta$$\overline{x}$ = `r myround(summary(mean.devtime.brms.em.contrast)[3,3],2)` \[`r myround(summary(mean.devtime.brms.em.contrast)[3,4],2)`, `r myround(summary(mean.devtime.brms.em.contrast)[3,5],2)`; @fig-one). We also found that individuals raised on a poor diet required more time to develop than those raised on a good diet (Estimate = `r myround(mean.devtime.brms_fixed[[3,4]],2)`, \[`r myround(mean.devtime.brms_fixed[[3,6]],2)`, `r myround(mean.devtime.brms_fixed[[3,7]],2)`\]).

# Discussion


\newpage

# References {.unnumbered}

::: {#refs}
:::

```{r}
#| echo: false
#| results: asis
block_section(
  prop_section(
    page_size = page_size(orient = "portrait"),
    type = "continuous"
  )
)
```

```{r}
#| echo: false
#| results: asis
#| warning: FALSE
#| label: tbl-two
#| tbl-cap: Phenotypic variance partitioning of four traits for female and male European earwig (*Forficula auricularia*) families raised on either a poor or good diet at low, medium, or high density. P^2^~RN~ is the proportion of the phenotypic variance arising from average plastic responses to to the nutritional environment, H^2^~RN~ is the broad-sense heritability of the trait when fully accounting for its reaction norm, and T^2^~RN~ is the proportion of the phenotypic variance explained by the plastic and genetically variable reaction norm. Numbers in brackets are 95% credible intervals (CrIs).

my_header <- data.frame(
  col_keys = c("variable", "f.mean.dev", "f.mean.pro", "f.mean.for", "f.mean.relfor", "break1", "m.mean.dev", "m.mean.pro", "m.mean.for", "m.mean.relfor"),
  line2 = c("","","","","", "break1","", "","", ""),
  stringsAsFactors = FALSE)

flextable(plasticity.table,col_keys = c("variable", "f.mean.dev", "f.mean.pro", "f.mean.for", "f.mean.relfor", "break1", "m.mean.dev", "m.mean.pro", "m.mean.for", "m.mean.relfor")) %>%
  #align(align = "right", part = "body") %>%
  flextable::set_header_df(
    mapping = my_header,
    key = "col_keys"
  ) %>%
  flextable::set_header_labels(variable="", f.mean.dev="Development time", f.mean.pro="Pronotum length", f.mean.for="Forceps length", f.mean.relfor="Relative forceps length", "break1", m.mean.dev="Development time", m.mean.pro="Pronotum length", m.mean.for="Forceps length", m.mean.relfor="Relative forceps length",top=FALSE) %>%
  flextable::add_header(variable = "", f.mean.dev = "Females", f.mean.pro = "Females", f.mean.for = "Females", f.mean.relfor = "Females", break1="", m.mean.dev = "Males", m.mean.pro = "Males", 
             m.mean.for ="Males", m.mean.relfor = "Males", top = TRUE) %>%
  merge_h(part = "header") %>%
  flextable::compose(part = "body", i= c(2, 6, 10), j =1, value = as_paragraph(("P"), as_sup("2"), as_sub("RN"))) %>%
    flextable::compose(part = "body", i= c(3, 7, 11), j =1, value = as_paragraph(("H"), as_sup("2"), as_sub("RN"))) %>%
    flextable::compose(part = "body", i= c(4, 8, 12), j =1, value = as_paragraph(("T"), as_sup("2"), as_sub("RN"))) %>%
  hline(i=1, j=c(2:5, 7:10), part="header",border=fp_border(color="black", width=1.5)) %>%
  hline(i=2, j=c(1:10), part="header",border=fp_border(color="black", width=1.5)) %>%
  merge_at(i = 1, j = c(1:2), part = "body") %>%
  merge_at(i = 5, j = c(1:2), part = "body") %>%
  merge_at(i = 9, j = c(1:2), part = "body") %>%
  flextable::bold(part="header") %>% 
  autofit() %>%
  fit_to_width(max_width = 9)
```

```{r}
#| echo: false
#| results: asis
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    type = "continuous"
  )
)
```

\newpage

```{r}
#| echo: false
#| results: asis
block_section(
  prop_section(
    page_size = page_size(orient = "landscape"),
    type = "continuous"
  )
)
```

##Figures

![Mean (±95% CrI) trait sizes of female and male earwigs raised on either a poor or good diet at low, medium, or high density. * above bracket denotes that the 95% CrI of the mean difference between two density levels did not include zero whereas NS denotes that the 95% CrI of the mean difference did include zero. Sample sizes are given below data points.](figure_1.jpg){#fig-one}
